\section{Introduction}
\label{sec:introduction}

Coding agents consume repository-local instruction files---\texttt{AGENTS.md}, Cursor rules, Claude skills, Copilot instruction packs---as authoritative context at task time.
Practitioners and researchers often analyze these files as if they were human-facing documentation whose truth is fixed at commit time.
We argue that this framing is insufficient: machine-consumed instruction files are \textbf{late-binding artifacts} whose semantics split across two channels.

\paragraph{Central claim.}
Machine-consumed instruction files are not ordinary documentation.
They operate through (1) a \emph{directive channel} that strongly shapes agent behavior and (2) a \emph{referential channel} whose \emph{static truth} is only weakly coupled to task outcomes because references are resolved against the live repository at use time.

\paragraph{Empirical program.}
We report a multi-stage empirical program on a frozen laboratory corpus:
longitudinal reconstruction and survival analysis (RQ1--RQ2),
observational integrity and lifecycle dynamics (RQ3--RQ4),
confirmatory audits of born-stale false claims,
human-validated agent-maintenance attribution (P4),
and a controlled agent experiment comparing truthful, confirmed-false, and no-instruction conditions (RQ5 A/B/C).

\paragraph{Contributions.}
\begin{itemize}
  \item A conceptual \emph{late-binding model} with explicit constructs (directive vs.\ referential channels, static truth, runtime resolution, causal load-bearing references).
  \item Observational evidence that post-verification reference decay is negligible in our audited cohort (0/121 adjusted genuine decay) while born-false claims at creation are prevalent (1200/1405 confirmed false; 85.4\%).
  \item Agent trace evidence that instructions are read (128/128) and often followed (72.3--77.8\% by condition), amplifying edit scope ($\sim$100 vs $\sim$2 files modified), without a measurable success difference between truthful and false referential content on paired triplets ($\Delta$ = 0.00~pp; McNemar $p = 1.0$).
  \item A reproducibility bundle mapping each claim to frozen exports (\path{exports/paper_synthesis/late_binding_evidence_table.csv}).
\end{itemize}

\paragraph{Paper organization.}
\todo{One-sentence roadmap.}
