\section{Results}
\label{sec:results}

We organize results by research question.
All values below are copied from frozen exports; see Table~\ref{tab:evidence-map} and \path{exports/paper_synthesis/late_binding_evidence_table.csv}.

\input{tables/evidence-summary}

\subsection{RQ1--RQ2: Static reference integrity}
\paragraph{Post-verification decay.}
Of 121 post-verification failure events audited, adjusted genuine decay count is \textbf{0/121} (0.0\%; Wilson 95\% CI: 0.0\%--3.1\%) (\path{rq2_failure_audit_summary.md}).
73.6\% of failures are classified as extractor artifacts.

\paragraph{Born-stale prevalence.}
Raw \texttt{genuine\_false\_claim} count: 1{,}405 (7.9\% of 17{,}747 born-stale cohort) (\path{born_stale_summary.md}).

\subsection{Confirmatory audits}
\paragraph{Confirmed false at creation.}
GFC confirmatory audit: \textbf{1{,}200 / 1{,}405} (85.4\%; Wilson 95\% CI: 83.5\%--87.2\%) (\path{gfc_confirmatory_summary.md}).
Adjusted born-stale false-claim rate: 6.76\% of cohort.

\paragraph{Path stability selection.}
Cited vs.\ uncited audit: in \textbf{85.4\%} of 2{,}259 matched pairs, cited path git churn $\leq$ uncited control (\path{cited_uncited_summary.md}).
Mean paired difference in churn: 0.44 commits (95\% bootstrap CI: $-0.21$--1.15; includes zero).

\subsection{P4: Agent maintenance attribution}
Precision 0.958; F1 0.9617 on $N=200$ human-reviewed commits (\path{p4_validation.md}).

\subsection{RQ5: Agent behavior and outcomes}

\subsubsection{Uptake funnel (A/B; $n=128$)}
\begin{itemize}
  \item \texttt{instruction\_read}: 128/128 (100\%).
  \item \texttt{instruction\_followed}: 47/65 (72.3\%) condition A; 49/63 (77.8\%) condition B.
  \item Task success: 8/65 (12.3\%) A; 8/63 (12.7\%) B.
\end{itemize}
Source: \path{rq5_uptake_analysis.md}.

\subsubsection{Behavioral amplification (paired triplets; $n=63$)}
Mean files modified: A = 99.7; B = 103.0; C = 1.7 (\path{rq5_abc_comparative_analysis.md}).
Compilation success: 100\% all conditions on triplets.

\subsubsection{Causal contrasts (paired triplets)}
\begin{itemize}
  \item \textbf{A $-$ B:} $\Delta$ success = 0.00~pp; cluster bootstrap 95\% CI [$-6.35$, $+6.35$]; McNemar $p = 1.0$.
  \item \textbf{A $-$ C:} $\Delta$ success = +4.76~pp; cluster bootstrap 95\% CI [$-12.70$, $+22.22$]; McNemar $p = 0.5811$.
  \item \textbf{B $-$ C:} $\Delta$ success = +4.76~pp (identical to A$-$C on overlap triplets where A and B success patterns match).
\end{itemize}
Success rates on triplets: A = 12.7\% (8/63); B = 12.7\% (8/63); C = 7.9\% (5/63).

\subsubsection{Condition C complete cohort ($n=105$)}
Aggregate success: 12/105 (11.4\%) (\path{exports/rq5_agent_impact_c/rq5_results.csv}).

\paragraph{Figures.}
\todo{Reference paper/figures copies of export PDFs for camera-ready.}
